Programming Language Foundations in Agda

### 2019-07-15 papers/scp/PLFA.tex
fix typo

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ieuramalischy; ten three-hour
  slots, comprising two hours of lecture followed by one hour of lab.
  Ten students completed the course, mostly doctoral students.  The
  course covered Parts~I and~II of PLFA, save students read chapter
  Lists on their own, and chapter Bisimilarity was skipped.

>>>>

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ierusalimschy; ten three-hour
  slots, comprising two hours of lecture followed by one hour of lab.
  Ten students completed the course, mostly doctoral students.  The
  course covered Parts~I and~II of PLFA, save students read chapter
  Lists on their own, and chapter Bisimilarity was skipped.
